\documentclass{article}
\begin{document}
\title{Problem Set #1}
\author{Alien Cipher}
\date{2025, 02, 22}
\maketitle
\section*{Problem #1}
\textbf {If a and b are two even integers, then a + b is even.} \\
\textbf{Solution:} \\
Direct proof:
Since a and b are two even integers, there exist two integers x and y such that a = 2x and b = 2y.\\
Then, a + b = 2x + 2y = 2(x + y),\\
Since (x + y) is an integer, a + b must be an even integer.

\section*{Problem #2}
\textbf {Prove that $\sqrt{2}$ is irrational.}\\
\textbf{Solution:}\\
Prove by contradiction:
Assume $\sqrt{2}$ is rational, there exists $\frac{p}{q}$ = $\sqrt{2}$ such that p and q are integers, p and q have no common divisor. \\
Calculation steps:
\[ \frac{p}{q} = \sqrt{2}\] \\
\[\Leftrightarrow \frac{p^2}{q^2} = 2\]\\
\[ \Leftrightarrow p^2 = 2q^2\] \\
Since  $p^2 = 2q^2$, $p^2$ must be even, so p must be even as well, there exist an integer k such that p = 2k. So, $p^2 = (2k)^2$
\[ \Leftrightarrow (2k)^2 = 2q^2\]
\[ \Leftrightarrow 2k^2 = q^2 \] (This implies that both $p^2$ and $q^2$ contain a common divisor 2, leads to a contradiction) \\
Therefore, $\sqrt{2}$ must be irrational.

\section*{Problem #3}
\textbf{Prove that if $n^2$ is even, then n is even.}\\
\textbf{Solution:}\\
Prove by contrapositve:
Rewrite the predicate as ``if n is odd, then $n^2$ is odd.``
Since n is odd, there exists an integer k such that n = 2k + 1. \\
\[n^2 = (2k + 1)^2 = 4k^2 + 4k + 1 = 2(2k^2 + 2k) + 1\]
Since $2k^2 + 2k$ is an integer, $n^2$ must be odd, proving the predicate. Therefore, the  original predicate is proven.

\section*{Problem #4}
\textbf{Show that 1 + 2 + 3 + ... + n = $\frac{n(n+1)}{2}$}\\
\textbf{Solution:}
Prove by mathematical induction.\\
1. Base case, where n = 1, $\frac{1(1+1)}{2} = 1$ (P(n)).\\
2. Induction  Hypothesis:\\
Assume P(n) is true for an arbitrary natural number k, that:\\
1 + 2 + 3 + ... + k = $\frac{k(k+1)}{2}$ = P(k). \\
3. Incduction steps:\\
Prove that if P(k) is true, then P(k + 1) must also be true.\\
1 + 2 + 3 + ... + k + (k + 1) = $\frac{k(k+1)}{2} + k + 1$\\
$\frac{k(k+1)}{2} + k + 1 = (\frac{k}{2} + 1)(k + 1) = \frac{k+2}{2}(k + 1) = \frac{k + 2(k + 1)}{2} = \frac{(k + 1)((k + 1) + 1)}{2}$ \\
Since P(k + 1) is true, the original predicate is proved. \\

\end{document}


